All watched over by machines of loving grace

### 2021-06-25 paper/paper.tex
paper: finished off section on HOL

Supervisionary implements a version of Gordon's higher-order logic (or HOL, henceforth), a close relative of Church's Simple Theory of Types that extends Church's system with top-level polymorphism.
We describe HOL here, introducing enough material for the reader to understand the remainder of the paper---motivating HOL or describing its expressiveness is outside of the scope of this paper.

@@

The set of primitive type-formers and constants defines an implicit \deffont{theory}.
Our version of HOL also includes two \emph{primitive definitional} principles for extending this theory with new defined constants and types, respectively.
Specifically, for a previously-undefined constant $\mathtt{C}$ and a term $r : \tau$ where $fv(r) = \{\}$ the constant $\mathtt{C}$ with declared type $\tau$ is added to the theory, as is an additional axiom $\{\} \vdash \mathtt{C} = r$.
TODO: type-definition

>>>>

Supervisionary implements a version of Gordon's higher-order logic (or HOL, henceforth), a close relative of Church's Simple Theory of Types.
We briefly describe HOL here.
Motivating HOL or describing its expressiveness is beyond the scope of this paper.

@@

The set of primitive type-formers and constants defines an implicit \deffont{theory}.
Our version of HOL also includes two \emph{primitive definitional} principles for extending this theory with new defined constants and types, respectively.

For a previously-undefined constant $\mathtt{C}$ and a term $r : \tau$ where $fv(r) = \{\}$ the constant $\mathtt{C}$ with declared type $\tau$ is added to the theory, as is an additional axiom $\{\} \vdash \mathtt{C} = r$.

New types are ``carved out'' of non-empty subsets of existing types.
Given an existing type $\tau$ and a predicate $p : \tau \Rightarrow \mathtt{bool}$ we introduce a new type $\tau'$ whenever $\{\} \vdash \xsts{x_\tau}p(x_\tau)$ holds.
In addition, two new constants are entered into the global theory---$\mathtt{in}_{\tau'}$ with type $\tau \Rightarrow \tau'$ and $\mathtt{out}_{\tau'}$ with type $\tau' \Rightarrow \tau$, respectively---representing \deffont{injection} and \deffont{projection} functions for the new type.
These two functions are related by also entering $\{\} \vdash \fall{x_\tau}p(x_\tau) \longrightarrow out_{\tau'}(in_{\tau'}(x_\tau)) = x_\tau$ and $\{\} \vdash \fall{x_{\tau'}}in_{\tau'}(out_{\tau'}(x_{\tau'})) = x_{\tau'}$ as additional axioms.
